manuscript

### 2023-11-21 scripts/manuscript.qmd
Data Visualizations
 Boxplot by gender

```{r}
#| include: FALSE
library(tidyverse)
library(here)
library(rio)
library(psych)
library(janitor)
```

@@

```{r}
#for ben to do later: create summarize data frames to create into a table
```
# Introduction

@@

To measure different aspects of student-teacher trust interactions, items were modified from Ledbetter and Vik’s (2012) Parental Privacy Invasions Scale (PPIS) and Levine and McCornack’s (1991) Suspicion Scale.

### Modified Parental Privacy Invasions Scale
Eleven items were adapted from the Parental Privacy Invasions Scale to reflect teacher, rather than parental, interactions. Each item was measured on a five-point Likert scale, ranging from 0 to 4, with response options including, “Never”, “Rarely”, “Often”, “Sometimes”, and “Always”.

Three items were modified the Parental Invasive Behavior subscale of the PPIS to measure student perceptions of invasive behaviors from their teachers. One example item from this subscale is, “My teachers demand that I change my behavior in some area of my life.”

The other 8 modified items came from the Children’s Defensive Behavior subscale, which captured the young adults’ self-reports of behaviors to safeguard their privacy from their teachers. An example of an item from this subscale is, “ I avoid going to see my teacher outside of normal school/class hours. (such as before or after class, during break, before or after school tutoring).”

@@

Twelve items were adapted from the Suspicion Scale to capture young adults' suspicion toward their teachers. Each item was measured on a seven-point Likert scale, ranging from 0-6, with response options including, "Strongly Disagree", "Somewhat Disagree", "Disagree", "Neither Agree nor Disagree", "Somewhat Agree", "Agree", and "Strongly Agree". Example items from the scale include, "Basically I am a trusting person", and "Most teachers follow the saying "honesty is the best policy."

>>>>

```{r}
#| include: FALSE
library(tidyverse)
library(here)
library(rio)
library(psych)
library(janitor)
library(ggplot2)
```

@@

```{r}
#for ben to do later: create summarize data frames to create into a table
```

#Data Visualizations

```{r boxplot-gender-ppis-1-score, warning=FALSE, echo=FALSE}

ggplot(communication, aes(gender, ppis_1_score, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
  labs(x = "Gender",
       y = "Parental Invasive Behaviors Score",
       title = "Boxplot of Parental Invasive Behaviors Score by Gender")

```

```{r boxplot-gender-ppis-2-score, warning=FALSE, echo=FALSE}

ggplot(communication, aes(gender, ppis_2_score, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
  labs(x = "Gender",
       y = "Student Defensive Behaviors Score",
       title = "Boxplot of Student Defensive Behaviors Score by Gender")

```

```{r boxplot-gender-ppis-total, warning=FALSE, echo=FALSE}

ggplot(communication, aes(gender, ppis_total, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
  labs(x = "Gender",
       y = "Parental Privacy Invasion Scale Total",
       title = "Boxplot of Parental Privacy Invasion Scale Total by Gender")

```

```{r boxplot-gender-ss-score, warning=FALSE, echo=FALSE}

ggplot(communication, aes(gender, ss_score, fill=gender)) +
  geom_boxplot() + 
  theme(legend.position="none") +
  labs(x = "Gender",
       y = "Suspicion Scale Score",
       title = "Boxplot of Suspicion Scale Score by Gender")

```

# Introduction

@@

To measure different aspects of student-teacher trust interactions, items were modified from Ledbetter and Vik's (2012) Parental Privacy Invasions Scale (PPIS) and Levine and McCornack's (1991) Suspicion Scale.

### Modified Parental Privacy Invasions Scale

Eleven items were adapted from the Parental Privacy Invasions Scale to reflect teacher, rather than parental, interactions. Each item was measured on a five-point Likert scale, ranging from 0 to 4, with response options including, "Never", "Rarely", "Often", "Sometimes", and "Always".

Three items were modified the Parental Invasive Behavior subscale of the PPIS to measure student perceptions of invasive behaviors from their teachers. One example item from this subscale is, "My teachers demand that I change my behavior in some area of my life."

The other 8 modified items came from the Children's Defensive Behavior subscale, which captured the young adults' self-reports of behaviors to safeguard their privacy from their teachers. An example of an item from this subscale is, " I avoid going to see my teacher outside of normal school/class hours. (such as before or after class, during break, before or after school tutoring)."

@@

Twelve items were adapted from the Suspicion Scale to capture young adults' suspicion toward their teachers. Each item was measured on a seven-point Likert scale, ranging from 0-6, with response options including, "Strongly Disagree", "Somewhat Disagree", "Disagree", "Neither Agree nor Disagree", "Somewhat Agree", "Agree", and "Strongly Agree". Example items from the scale include, "Basically I am a trusting person", and "Most teachers follow the saying"honesty is the best policy."
